---
title: "Description and choice data for the domain \"`r params$domain_name`\""
output: 
  pdf_document:
    citation_package: none
    includes:
      in_header: preamble.tex
params:
  i: 0
  domain_name: "colours"
  domain_filename: "colours"
  N: 0
---

\graphicspath{
  {../experiment/figures/}       % figures used in experiment
}

## Description of the choice domain `r params$i`, ```r params$domain_name```

The prompt question and the universe of five response options in the choice domain ```r params$domain_name``` are as follows.
The labels $a$, $b$, $c$, $d$ and $e$ were not displayed during the experiment and are indicated here to allow cross-referencing with data tables and visualizations below and results in the paper.

```{r echo=FALSE, results='asis'}
#domain_Rmd_filename <- here("paper/domain_tex",
#                            sprintf("%s.tex", params$domain_filename))
#out <- knitr::knit_child(domain_Rmd_filename, quiet = TRUE)
#knitr::asis_output(out)

#knitr::asis_output(readr::read_file(
#  here("paper/domain_tex", sprintf("%s.tex", params$domain_filename))
#))

knitr::asis_output(sprintf("\\input{../paper/domain_tex/%s.tex}", params$domain_filename))
```

The following figure is a screenshot from the actual experiment, with one of the 26 possible menus for this domain.

```{r, echo=FALSE}
screen_shot_filename <- sprintf("screenshot_%s.png", params$domain_filename)
Rmd_string <- sprintf("![Screenshot for domain %s](%s)",
                      params$domain_name, here("experiment/screenshots",
                                               screen_shot_filename))
knitr::asis_output(Rmd_string)
```

\pagebreak

## Choice data for domain `r params$i`, `r params$domain_name`

Table \ref{t:count_prop} shows choice counts and choice proportions for this choice domain.
For each menu $A$ and each object $x \in \{a,b,c,d,e\}$, $N_A(x)$ is the number of participants who chose object $x$ from menu $A$ and $\hat P_A(x)$ is the corresponding proportion of participants who chose $x$ from $A$.
When $x \notin A$, a dash is displayed.

\begin{table}\centering
```{r data_table, echo=FALSE, results='asis'}
count_proportion_table(params$N)
```
\caption{Observed choice counts and proportions.}
\label{t:count_prop}
\end{table}

The following figure displays choice proportions for all doubleton and tripleton menus in Barycentric coordinates.
See a full description of this graphical representation in the paper.
Each panel shows choice proportions for all doubleton and tripleton menus of a different tripleton subset of $\{a,b,c,d,e\}$.
The downward-pointed (blue) triangle shows the set of ternary choice proportions that are compatible with regularity and the three binary choice proportions, on the corresponding tripleton.
The upward-pointed (red) triangle shows the set of ternary choice proportions compatible with the multiplicative inequality and the three binary choice proportions.

```{r simplex_plots, echo=FALSE, fig.width=8, fig.height=10}
RanCh::bin_tern_MR_plot_all(params$N)
```

\bibliographystyle{plainnat}
\bibliography{bibliography}
