\documentclass[11pt,letter]{amsart}

\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage[abbr]{harvard}
%doublespace

\begin{document}

\title{Proposal for an experiment}
\author{William J. McCausland}
\date{Current version: \today.}

\maketitle

Tony Marley are planning an experiment to test random utility (and other hypotheses) in multiple domains.
We are currently at the brainstorming stage and would like reactions and feedback.

Given our research question, it is very important to observe choice probabilities on choice sets of different sizes (binary, ternary and $n$-ary choice).
Our current focus is testing random utility and other behavioural conditions for {\em population} rather than {\em individual} choice probabilities.

There would be about 20 {\em master sets} of five objects each.
Each master set would be a collection of similar objects from some domain --- see list of possible domains below.
Choice sets are subsets, with at least two elements, of some master set.
Each participant would see only one subset from each master set, and hence various subsets from different domains, and different participants would see different choice sets from the same master set.
For a master set of size five, there are 26 subsets of cardinality greater than or equal to two, and many (40?) participants would see (and choose from) each subset.

Some possible domains
\begin{enumerate}
	\item Perception (i.e. the sub-field of Psychology with that name)
	\begin{enumerate}
		\item Judging areas of rectangles (possible context effects)
	\end{enumerate}
	\item Aesthetic judgement (choice of favourite)
	\begin{enumerate}
		\item Unfamiliar art forms
		(e.g. Australian aboriginal art to Canadians, Canadian first nations art to Australians)
		\item Book descriptions (from Amazon or dust jacket)
		\item Film descriptions (from DVD cover, film catalogue)
		\item Exotic travel destinations
	\end{enumerate}
	\item Consumer choice
	\begin{enumerate}
		\item Objects with attributes (e.g. mobile phones)
		\item Transportation choice
	\end{enumerate}
	\item Policy options
	\begin{enumerate}
		\item Environment
	\end{enumerate}
\end{enumerate}

Some of the issues we have questions about:
\begin{enumerate}
	\item relevance of testing axioms with observed {\em population} choice probabilities
	\item feasibility and suitability of Pure Profile and Mechanical Turk (Amazon).
	\item design issues
	\item legal issues (copyright)
	\item academic ethics approval
	\item appropriate domains, ideas for different domains
\end{enumerate}

\end{document}
